A generalized definition of multidimensional item response theory parameters

### 2023-03-03 output/paper_draft/paper_M2PLM_parameters.Rmd
Changes the reference to the discrimination vector by its symbol

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.
We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of
the discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces.
Let's consider the model given by Equation \@ref(eq:M2PL-formulation),
where the latent traits and the parameters $a_i$ are expressed in the same basis
$`r LS_BASIS`$ in their respective spaces.

>>>>

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.
We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of
the discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces.
Let's consider the model given by Equation \@ref(eq:M2PL-formulation),
where the latent traits and the parameters $`r DISCR_VECTOR`$ are expressed
in the same basis $`r LS_BASIS`$ in their respective spaces.
